An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-12-02 paper/1.introduction.tex
add/reduce spaces

\begin{figure}[!t]
  \begin{minipage}{0.3\textwidth}
    \centering
    \includegraphics[height=3.5cm]{./fig/fig1.eps}
    \caption{Evaluating $phead$}
    \label{fig:eval-phead}
  \end{minipage}\hfill
  \begin{minipage}{0.7\textwidth}
    \centering
    \includegraphics[height=3.5cm]{./fig/fig2.eps}
    \caption{Evaluating $phead \circ phead \circ phead$}
    \label{fig:eval-comp-phead}
  \end{minipage}
\end{figure}

@@

One direct solution to avoid this repeated computation of $get$ is to compute the composition in a right associative manner. For instance, if we transform  $lp3$ to $rp3$:

\minusvspacetwo
\vspace{-4mm}
\[
rp3 = phead \circ (phead \circ phead)
\]
\minusvspacetwo

@@

\minusvspacetwo
 \[
 \mbox{\it bfoldr}~bx~\cdots = \cdots  (\mbox{\it bfoldr}~\cdots) \circ bx \cdots
 \]
 \minusvspacetwo

>>>>

\begin{figure}[!t]
  \begin{minipage}{0.3\textwidth}
    \centering
    \includegraphics[height=3.5cm]{./fig/fig1.eps}
    \caption{Evaluating $phead$}
    \label{fig:eval-phead}
  \end{minipage}\hfill
  \begin{minipage}{0.7\textwidth}
    \centering
    \includegraphics[height=3.5cm]{./fig/fig2.eps}
    \caption{Evaluating $phead \circ phead \circ phead$}
    \label{fig:eval-comp-phead}
  \end{minipage}
\end{figure}
\vspace*{-5.5mm}

@@

One direct solution to avoid this repeated $get$ computation is to compute compositions in a right associative manner. For instance, if we transform $lp3$ to $rp3$:\break

\minusvspacetwo
\vspace{-3mm}
\[
rp3 = phead \circ (phead \circ phead)
\]
\minusvspacetwo
\vspace{-0mm}

@@

\vspace{1mm}
\minusvspacetwo
 \[
 \mbox{\it bfoldr}~bx~\cdots = \cdots  (\mbox{\it bfoldr}~\cdots) \circ bx \cdots
 \]
 \minusvspacetwo
